Factors determining how catchments respond to forest cover change. Re-analysing global data sets.

### 2022-02-01 paper/Forest_and_Water/Forest_and_Water.tex
Figure 2 label corrected figure 4 modified with new data and all catchments under the same category

\usepackage{lineno} % add
  \linenumbers % turns line numbering on

\usepackage{graphicx}
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Factors determining how catchments respond to forest cover change. Re-analysing global data sets.},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% From pandoc table feature
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}

% Pandoc citation processing
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

\begin{frontmatter}

@@

  \begin{abstract}
  Three recent papers review and analyse large global datasets related to impacts of forest cover on streamflow. Using three different approaches, they all find a strong relationship between forestation/de-forestation and streamflow. However, the past approaches in the literature are variable and can be substantially improved in statistical rigour, and indicate different confounding factors on the impact of forestation. The data for these three papers were reviewed, combined and re-analysed to answer the following new and older questions: 1) How is streamflow impacted by the change in forest cover as a function of catchment area; 2) how is this relationship conditioned by the length of the study, and climate; and 3) are there other possible variables that impact the observed change in streamflow? Generalised additive models were used to run flexible regressions including multiple variables.
  Changes in forest cover cause changes in streamflow, however this change is different between deforestation and reforestation, and strongly affected by climate, with drier climates indicating larger changes in streamflow. Deforestation causes a 32\% greater change in flow compared to reforestation. Area of the catchment only affects the change in streamflow after log transformation, given the wide variety in the data from small scale paired watershed studies. Smaller studies dominate the database with 42\% of the data \textless{} 1 km2 and 65\% of the data \textless{} 10 km2. Length of the study and initial year of the study did not affect the change in flow, in contrast to other reported studies. Despite these findings, overall explained variance (38\%) is low due the quality of the inputs and additional unknown confounding factors.
  \end{abstract}

@@

\begin{longtable}[]{@{}lll@{}}
\toprule
Factor & Abbreviation & Definition \\
\midrule
\endhead
forest type & CF & coniferous forest \\
& BF & broadleaf forest \\
& MF & mixed forest \\
hydrological regime & RD & rain dominated \\
& SD & snow dominated \\
climate type & EL & energy limited \\
& WL & water limited \\
& EQ & equitant \\
precipitation data type & OB & observed \\
& SG & spatial gridded \\
& MD & modelled \\
assessment technique & PWE & paired watershed experiment \\
& QPW & quasi-paired watershed experiment \\
& HM & hydrological modelling \\
& EA & elastictity analysis \\
& SH & combined use of statistical methods \\
& & and hydrographs \\
\bottomrule
\end{longtable}

@@

The length of the study can be a variable influencing the change in flow (Filoso et al., 2017; e.g. Jackson et al., 2005), as for example, more mature plantations are thought to have smaller impacts on flow or regrowth might follow a ``Kuczera curve'' (Kuczera, 1987). Therefore, the length of the study calculate as the difference between the starting data and completion date of the different studies was extracted from the references provided by Zhang et al. (2017). The length of the study was already included in the data from Filoso et al. (2017), but these were checked against the original publications.

@@

\hypertarget{description-of-the-data}{%
\subsection{description of the data}\label{description-of-the-data}}

The overall dataset contains 309 observations of changes in flow, which includes the newly identified data sets and after removing identified duplicate data and lines with missing data. In contrast, the original dataset from Zhang et al. (2017) contained 312 catchments and the Filoso et al. (2017) study used 37 catchments (Table S2 in Filoso et al. (2017)). The overall distribution of changes in flow is highly skewed as is the distribution of changes in forest cover and Area. The values of changes in flow greater than 100\% and smaller than -100\% clearly create long tails on the change in flow distribution. Note also the large number of studies with 100\% forest cover reduction. Smaller catchments dominate the database with 42\% of the data from catchments \textless{} 1 km\textsuperscript{2} and 65\% of the data for catchments \textless{} 10 km\textsuperscript{2}.

@@

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.36}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.15}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.18}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.14}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.15}}@{}}
\caption{\label{tab:tabmodel1} Summary results of the first regression model predicting change in streamflow from change in forest cover and accounting for the direction of the change. The first three rows relate to the model using the original data base from Zhang et al.~(2017). The bottom three rows are the results of the model including the new data}\tabularnewline
\toprule
\begin{minipage}[b]{\linewidth}\centering
~
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Estimate
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Std. Error
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
t value
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Pr(\textgreater\textbar t\textbar)
\end{minipage} \\
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{\linewidth}\centering
~
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Estimate
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Std. Error
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
t value
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Pr(\textgreater\textbar t\textbar)
\end{minipage} \\
\midrule
\endhead
\textbf{(Intercept)} & 8.65 & 5.56 & 1.56 & 0.12 \\
\textbf{DeltaF\_perc\_pos} & 0.45 & 0.09 & 5.26 & 0 \\
\textbf{Forest\_Signincrease} & -29.17 & 5.79 & -5.04 & 0 \\
\textbf{(Intercept)} & 9.43 & 5.54 & 1.7 & 0.09 \\
\textbf{DeltaF\_perc\_pos} & 0.44 & 0.09 & 5.12 & 0 \\
\textbf{Forest\_Signincrease} & -36.54 & 5.59 & -6.53 & 0 \\
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.36}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.15}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.18}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.14}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.15}}@{}}
\caption{\label{tab:out-model3} Results of the model including Latitude and Longitude including new data}\tabularnewline
\toprule
\begin{minipage}[b]{\linewidth}\centering
~
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Estimate
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Std. Error
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
t value
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Pr(\textgreater\textbar t\textbar)
\end{minipage} \\
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{\linewidth}\centering
~
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Estimate
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Std. Error
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
t value
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Pr(\textgreater\textbar t\textbar)
\end{minipage} \\
\midrule
\endhead
\textbf{(Intercept)} & 10.13 & 6.01 & 1.69 & 0.09 \\
\textbf{DeltaF\_perc\_pos} & 0.45 & 0.09 & 5.22 & 0 \\
\textbf{Forest\_Signincrease} & -38.15 & 5.95 & -6.41 & 0 \\
\textbf{Latitude} & -0.04 & 0.09 & -0.4 & 0.69 \\
\textbf{Longitude} & 0.01 & 0.03 & 0.26 & 0.79 \\
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.36}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.15}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.18}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.14}}
  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.15}}@{}}
\caption{\label{tab:out-model4} Results of the model including the dryness index}\tabularnewline
\toprule
\begin{minipage}[b]{\linewidth}\centering
~
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Estimate
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Std. Error
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
t value
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Pr(\textgreater\textbar t\textbar)
\end{minipage} \\
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{\linewidth}\centering
~
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Estimate
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Std. Error
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
t value
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Pr(\textgreater\textbar t\textbar)
\end{minipage} \\
\midrule
\endhead
\textbf{(Intercept)} & 3.18 & 6.77 & 0.47 & 0.64 \\
\textbf{DeltaF\_perc\_pos} & 0.43 & 0.09 & 4.91 & 0 \\
\textbf{Forest\_Signincrease} & -37.43 & 5.68 & -6.59 & 0 \\
\textbf{Dryness} & 5.56 & 3.06 & 1.82 & 0.07 \\
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.15}}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.17}}
  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.46}}@{}}
\caption{\label{tab:drytable} catchments for which the dryness index \textgreater{} 4}\tabularnewline
\toprule
\begin{minipage}[b]{\linewidth}\centering
Latitude
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Longitude
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Watershed name
\end{minipage} \\
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{\linewidth}\centering
Latitude
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Longitude
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Watershed name
\end{minipage} \\
\midrule
\endhead
34.67 & -111.7 & Beaver Creek, AZ \#3-2 \\
36.4 & -120.4 & Cantua \\
34.43 & -112.3 & White Spar, Ariz., U.S.A, B \\
32.74 & -111.5 & Natural DRDages, Ariz., U.S.A,
A \\
\bottomrule
\end{longtable}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-andreassian2004}{}}%
Andréassian, V., 2004. Waters and forests: From historical controversy to scientific debate. Journal of Hydrology 291, 1--27. doi:\url{https://doi.org/10.1016/j.jhydrol.2003.12.015}

>>>>

\usepackage{lineno} % add
  \linenumbers % turns line numbering on
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\usepackage{graphicx}
\usepackage{booktabs} % book-quality tables
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{longtable}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Factors determining how catchments respond to forest cover change. Re-analysing global data sets.},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

% Pandoc citation processing

% Pandoc header

\begin{document}
\begin{frontmatter}

@@

  \begin{abstract}
  Changes in forest cover cause changes in streamflow, however this change is different between deforestation and reforestation, and strongly affected by climate, with drier climates indicating larger changes in streamflow. Deforestation causes a 32\% greater change in flow compared to reforestation. Area of the catchment only affects the change in streamflow after log transformation, given the wide variety in the data from small scale paired watershed studies. Smaller studies dominate the database with 42\% of the data \textless{} 1 km2 and 65\% of the data \textless{} 10 km2. Length of the study and initial year of the study did not affect the change in flow, in contrast to other reported studies. Despite these findings, overall explained variance (38\%) is low due the quality of the inputs and additional unknown confounding factors.
  Three recent papers review and analyse large global datasets related to impacts of forest cover on streamflow. Using three different approaches, they all find a strong relationship between forestation/de-forestation and streamflow. However, the past approaches in the literature are variable and can be substantially improved in statistical rigour, and indicate different confounding factors on the impact of forestation. The data for these three papers were reviewed, combined and re-analysed to answer the following new and older questions: 1) How is streamflow impacted by the change in forest cover as a function of catchment area; 2) how is this relationship conditioned by the length of the study, and climate; and 3) are there other possible variables that impact the observed change in streamflow? Generalised additive models were used to run flexible regressions including multiple variables.
  \end{abstract}

@@

\begin{longtable}[]{@{}lll@{}}
\toprule
Factor & Abbreviation & Definition\tabularnewline
\midrule
\endhead
forest type & CF & coniferous forest\tabularnewline
& BF & broadleaf forest\tabularnewline
& MF & mixed forest\tabularnewline
hydrological regime & RD & rain dominated\tabularnewline
& SD & snow dominated\tabularnewline
climate type & EL & energy limited\tabularnewline
& WL & water limited\tabularnewline
& EQ & equitant\tabularnewline
precipitation data type & OB & observed\tabularnewline
& SG & spatial gridded\tabularnewline
& MD & modelled\tabularnewline
assessment technique & PWE & paired watershed experiment\tabularnewline
& QPW & quasi-paired watershed experiment\tabularnewline
& HM & hydrological modelling\tabularnewline
& EA & elastictity analysis\tabularnewline
& SH & combined use of statistical methods\tabularnewline
& & and hydrographs\tabularnewline
\bottomrule
\end{longtable}

@@

The length of the study can be a variable influencing the change in flow (e.g.~Jackson et al., 2005; Filoso et al., 2017), as for example, more mature plantations are thought to have smaller impacts on flow or regrowth might follow a ``Kuczera curve'' (Kuczera, 1987). Therefore, the length of the study calculate as the difference between the starting data and completion date of the different studies was extracted from the references provided by Zhang et al. (2017). The length of the study was already included in the data from Filoso et al. (2017), but these were checked against the original publications.

@@

\hypertarget{description-of-the-data}{%
\subsection{Description of the data}\label{description-of-the-data}}

The overall dataset contains 309 observations of changes in flow, which includes the newly identified data sets and after removing identified duplicate data and lines with missing data. In contrast, the original dataset from Zhang et al. (2017) contained 312 catchments and the Filoso et al. (2017) study used 37 catchments (Table S2 in Filoso et al. (2017)). The overall distribution of changes in flow is highly skewed as is the distribution of changes in forest cover and Area. The values of changes in flow greater than 100\% and smaller than -100\% clearly create long tails on the change in flow distribution. Note also the large number of studies with 100\% forest cover reduction. Smaller catchments dominate the database with 42\% of the data from catchments \textless{} 1 km\textsuperscript{2} and 65\% of the data for catchments \textless{} 10 km\textsuperscript{2} (Figure 1).

@@

In addition, this shows that for the data related to forest decreases, there is almost always a positive flow change (Figure 2). In other words, flow almost always increased. However, for increases in forest cover, this is not the case, and flow can both increase and decrease. However in both cases the variability in the reported change in flow increases with the increase in forest cover change.

@@

\begin{longtable}[]{@{}ccccc@{}}
\caption{\label{tab:tabmodel1} Summary results of the first regression model predicting change in streamflow from change in forest cover and accounting for the direction of the change. The first three rows relate to the model using the original data base from Zhang et al.~(2017). The bottom three rows are the results of the model including the new data.}\tabularnewline
\toprule
\begin{minipage}[b]{0.31\columnwidth}\centering
~\strut
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\centering
Estimate\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\centering
Std. Error\strut
\end{minipage} & \begin{minipage}[b]{0.12\columnwidth}\centering
t value\strut
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\centering
Pr(\textgreater\textbar t\textbar)\strut
\end{minipage}\tabularnewline
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{0.31\columnwidth}\centering
~\strut
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\centering
Estimate\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\centering
Std. Error\strut
\end{minipage} & \begin{minipage}[b]{0.12\columnwidth}\centering
t value\strut
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\centering
Pr(\textgreater\textbar t\textbar)\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{(Intercept)}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
8.65\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
5.56\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
1.56\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.12\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{DeltaF\_perc\_pos}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.45\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
0.09\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
5.26\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{Forest\_Signincrease}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
-29.17\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
5.79\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
-5.04\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{(Intercept)}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
9.43\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
5.54\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
1.7\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.09\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{DeltaF\_perc\_pos}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.44\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
0.09\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
5.12\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{Forest\_Signincrease}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
-36.54\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
5.59\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
-6.53\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}ccccc@{}}
\caption{\label{tab:out-model3} Results of the model including Latitude and Longitude including new data}\tabularnewline
\toprule
\begin{minipage}[b]{0.31\columnwidth}\centering
~\strut
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\centering
Estimate\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\centering
Std. Error\strut
\end{minipage} & \begin{minipage}[b]{0.12\columnwidth}\centering
t value\strut
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\centering
Pr(\textgreater\textbar t\textbar)\strut
\end{minipage}\tabularnewline
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{0.31\columnwidth}\centering
~\strut
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\centering
Estimate\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\centering
Std. Error\strut
\end{minipage} & \begin{minipage}[b]{0.12\columnwidth}\centering
t value\strut
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\centering
Pr(\textgreater\textbar t\textbar)\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{(Intercept)}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
10.13\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
6.01\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
1.69\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.09\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{DeltaF\_perc\_pos}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.45\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
0.09\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
5.22\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{Forest\_Signincrease}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
-38.15\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
5.95\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
-6.41\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{Latitude}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
-0.04\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
0.09\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
-0.4\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.69\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{Longitude}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.01\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
0.03\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
0.26\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.79\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}ccccc@{}}
\caption{\label{tab:out-model4} Results of the model including the dryness index}\tabularnewline
\toprule
\begin{minipage}[b]{0.31\columnwidth}\centering
~\strut
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\centering
Estimate\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\centering
Std. Error\strut
\end{minipage} & \begin{minipage}[b]{0.12\columnwidth}\centering
t value\strut
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\centering
Pr(\textgreater\textbar t\textbar)\strut
\end{minipage}\tabularnewline
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{0.31\columnwidth}\centering
~\strut
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\centering
Estimate\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\centering
Std. Error\strut
\end{minipage} & \begin{minipage}[b]{0.12\columnwidth}\centering
t value\strut
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\centering
Pr(\textgreater\textbar t\textbar)\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{(Intercept)}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
3.18\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
6.77\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
0.47\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.64\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{DeltaF\_perc\_pos}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.43\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
0.09\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
4.91\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{Forest\_Signincrease}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
-37.43\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
5.68\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
-6.59\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\centering
\textbf{Dryness}\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
5.56\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\centering
3.06\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
1.82\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.07\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}ccc@{}}
\caption{\label{tab:drytable} catchments for which the dryness index \textgreater{} 4}\tabularnewline
\toprule
\begin{minipage}[b]{0.14\columnwidth}\centering
Latitude\strut
\end{minipage} & \begin{minipage}[b]{0.15\columnwidth}\centering
Longitude\strut
\end{minipage} & \begin{minipage}[b]{0.42\columnwidth}\centering
Watershed name\strut
\end{minipage}\tabularnewline
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{0.14\columnwidth}\centering
Latitude\strut
\end{minipage} & \begin{minipage}[b]{0.15\columnwidth}\centering
Longitude\strut
\end{minipage} & \begin{minipage}[b]{0.42\columnwidth}\centering
Watershed name\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.14\columnwidth}\centering
34.67\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
-111.7\strut
\end{minipage} & \begin{minipage}[t]{0.42\columnwidth}\centering
Beaver Creek, AZ \#3-2\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering
36.4\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
-120.4\strut
\end{minipage} & \begin{minipage}[t]{0.42\columnwidth}\centering
Cantua\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering
34.43\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
-112.3\strut
\end{minipage} & \begin{minipage}[t]{0.42\columnwidth}\centering
White Spar, Ariz., U.S.A, B\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering
32.74\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
-111.5\strut
\end{minipage} & \begin{minipage}[t]{0.42\columnwidth}\centering
Natural DRDages, Ariz., U.S.A,
A\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-andreassian2004}{}%
Andréassian, V., 2004. Waters and forests: From historical controversy to scientific debate. Journal of Hydrology 291, 1--27. doi:\href{https://doi.org/https://doi.org/10.1016/j.jhydrol.2003.12.015}{https://doi.org/10.1016/j.jhydrol.2003.12.015}
